%%% activity to draw and calculate are and circumference of circles and sectors.
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End: 

\documentclass[12pt]{article}



\pdfpagewidth 8.5in
\pdfpageheight 11in


\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{color}
\usepackage{graphpap}
\usepackage{array}
\usepackage{fancyhdr}
\usepackage{geometry}

\geometry{
letterpaper,
 textwidth=185mm,
 textheight=24cm,
 left=20mm,
 top=20mm,
 }
 
%\setlength\topmargin{0cm}
%\setlength\headheight{0cm}
%\setlength\headsep{5mm}
%\setlength\textheight{22cm}
%\setlength\textwidth{175mm}
%\setlength\oddsidemargin{0in}
%\setlength\evensidemargin{0in}
%\setlength\parindent{0in}
%\setlength\parskip{1mm}

\input xy
\xyoption{all}


\pagestyle{fancyplain}
\lhead{Name:}
\chead{Date:}
\rhead{Period: }
\lfoot{Physics}
\rfoot{RH Cox}

\newcommand{\GUESS}[1]
{
\item #1

\setlength\extrarowheight{ 4 mm}
\begin{tabular} {| p{20mm} | p{6cm} | p{7cm} |}
\hline
 Given		&	 	&  Picture and Process \\
\hline
Unknowns 	&  	&  \\
\cline{1-2}
Equation 		&  	  &\\
\cline{1-2}
Solution 		&	  &	  \\
\hline
\end{tabular}
}

\newcommand{\MPS}
{
\, \frac{m}{s}
}

\newcommand{\MPSS}
{
\, \frac{m}{s^2}
}
\newcommand{\kg}
{
\, kg
}

\newcommand{\meters}
{
\, m
}



\begin{document}

\begin{center}
\Large
\bfseries
Uniform Circular Motion
\end{center}


\renewcommand\labelenumi{\Roman{enumi}.}
\renewcommand\labelenumii{\Alph{enumii}.}
\renewcommand\labelenumiii{\arabic{enumiii}.}
\renewcommand\labelenumiv{ \alph{enumiv}.}

\large
%\normalsize


\begin{enumerate}

	\GUESS{A mass is being twirled in a circle of radius  $0.4 \meters$.  It makes 10 revolution every second. Calculate the angular velocity.}
	\GUESS{A mass is being twirled in a circle of radius  $0.7 \meters$.  It makes 16 revolution every second. Calculate the angular velocity. }
	\GUESS{A mass is being twirled in a circle of radius  $0.4 \meters$.  It makes 10 revolution every second. Calculate the linear velocity.}
	\GUESS{A mass is being twirled in a circle of radius  $0.7 \meters$.  It makes 15 revolution every second. Calculate the linear velocity.}
	\newpage
	\GUESS{A $0.2\kg$  mass is being twirled in a circle of radius  $0.4 \meters$.  It makes 10 revolution every second. Calculate the centripetal force.}
	\GUESS{A $0.4\kg$ mass is being twirled in a circle of radius  $0.7 \meters$.  It makes 16 revolution every second. Calculate the  centripetal force.}
	\GUESS{AA $0.2\kg$  mass is being twirled in a circle of radius  $0.4 \meters$.  It makes 10 revolution every second. Calculate the centripetal acceleration?}
	\GUESS{A $0.4\kg$ mass is being twirled in a circle of radius  $0.7 \meters$.  It makes 16 revolution every second. Calculate the  centripetal accelertion}

\end{enumerate}



\end{document}